Robotic Manipulator Path Planning Utilizing Interpolated 3D Voxel-Based Obstacle Avoidance Method

### 2023-11-15 Articles/Article 1/main.tex
rotation primary task description

\documentclass[]{article}

@@

\add{
	-orientation error \\ 
	- p = v w \\
	- shorten
}

@@

\begin{equation} 
	\vec{v}_{ATT} = \frac{\vec{x}_{EE} - \vec{x}_g}{||\vec{x}_{EE} - \vec{x}_g||} \times \frac{\arctan(k_{sigm} \; ||\vec{x}_{EE} - \vec{x}_g||) }{pi/2}
	\label{eqq: v_att}
\end{equation}

In the above equation (eq.~\ref{eqq: v_att}), $\vec{v}_{ATT}$  represents the end effector's translational velocity towards the target, combining direction and magnitude. The terms $\vec{x}_{EE}$ and $\vec{x}_g$ denote the current and goal positions of the EE, respectively, in Cartesian coordinates. The unit vector calculation, $\frac{\vec{x}_{EE}-\vec{x}_g}{||\vec{x}_{EE}-\vec{x}_g||}$, ensures motion directed towards the target. Finally, the sigmoid function, particularly the arctangent component, modulates this velocity to avoid overshooting, balancing speed and precision. The constant $k_{sigm}$ allows us to set how close to the goal does the robot EE start slowing down.

>>>>

% !TeX spellcheck = en_US
\documentclass[]{article}

\usepackage{amsmath, xparse}

@@

@@

\begin{equation} 
	\vec{v}_{ATT} = \frac{\vec{x}_{EE} - \vec{x}_g}{||\vec{x}_{EE} - \vec{x}_g||} \times \frac{\arctan(k_{sigm} \; ||\vec{x}_{EE} - \vec{x}_g||) }{pi/2}
	\label{eq: v_att}
\end{equation}

In the above equation (eq.~\ref{eq: v_att}), $\vec{v}_{ATT}$  represents the end effector's translational velocity towards the target, combining direction and magnitude. The terms $\vec{x}_{EE}$ and $\vec{x}_g$ denote the current and goal positions of the EE, respectively, in Cartesian coordinates. The unit vector calculation, $\frac{\vec{x}_{EE}-\vec{x}_g}{||\vec{x}_{EE}-\vec{x}_g||}$, ensures motion directed towards the target. Finally, the sigmoid function, particularly the arctangent component, modulates this velocity to avoid overshooting, balancing speed and precision. The constant $k_{sigm}$ allows us to set how close to the goal does the robot EE start slowing down.

The rotational velocity error of the EE is needed for ensuring goal orientation of the EE. In our approach, orientations are depicted using rotation matrices. Specifically, \( R \) represents the current EE orientation, while \( gR \) signifies the goal EE orientation. The disparity between these orientations is encapsulated by the relative rotation matrix \( dR \). This matrix is formulated by multiplying the goal orientation matrix \( gR \) with the transpose of the current orientation matrix \( cR^{T} \). To ensure that it represents a pure rotation without any scaling we than normalize the so gotten matrix .

\begin{equation}
	dR = \frac{gR \cdot cR^{T}}{||gR \cdot cR^{T}||}
	\label{eq: rot_diff_mat}
\end{equation}

The relative rotation matrix value is converted into a quaternion, which is then logarithmically transformed to represent the rotational error vectorially:

\begin{equation}
	dR \mapsto dQ = a + b \, i + c \, j + d \, k
	\label{eq: quat_mapsto}
\end{equation}

\begin{equation}
	dQl = 2 \cdot \log(dQ) = al + bl \, i + cl \, j + dl \, k
	\label{eq:quat_log}
\end{equation}

The components of this quaternion, excluding the real part, form the rotational error vector \( \omega \):

\begin{equation}
	\vec{\omega} =
	\begin{bmatrix}
		bl \\
		cl \\
		dl
	\end{bmatrix}
	\label{eq:rot_error_vector}
\end{equation}

To get the full velocity of the end effector (EE), \( \mathrm{velocityEE} \), we combines translational and rotational velocities, which we scale using proportional gains \( k_p \) and \( k_r \).

\begin{equation}
	\vec{\mathrm{velocityEE}} = 
	\begin{bmatrix}
		k_p \times \vec{v}   \\
		k_{\omega} \times \vec{\omega}
	\end{bmatrix}
	\label{eq:ee_velocity}
\end{equation}
